A new breeding crossover approach for evolutionary algorithms

### 2023-09-21 paper.tex
Proposal Update 2

>>>>

    As shown in Figure~\ref{fig.contrange_crossover}, Continuous Range Crossover, we generate a template with the chromosome values of the parents. We use this template for the generation of all their children. In the following experiment results shown in this document, we have generated two children per couple reproduction, the same way the One Point Crossover strategy does. This offspring number generated has the purpose of maintaining a balance in the population created by the reproduction operator in both proposals.
